---
title: "Lab 05: Fixing merge conflicts and computing probabilities"
subtitle: "Due: Sat, Feb 27 at 11:59pm ET"
author: ""
date: ""
editor_options: 
  chunk_output_type: console
output:
  pdf_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Packages

```{r load-packages}
library(tidyverse)
``` 

# Data

The data comes from a cohort study of collegiate athletes using the National 
Collegiate Athletic Association (NCAA) Injury Surveillance System; certified athletic trainers recorded data during the 1997–2000 academic years.

The objective of the study was to compare sex differences regarding the 
incidence of concussions among collegiate athletes across three seasons in various sports.

```{r load-data}
concussion <- read_table("http://users.stat.ufl.edu/~winner/data/concussion.dat",col_names = FALSE)
```

# Exercises

## Exercise 1

```{r ex_1}
```


# References

"Datasets". Users.Stat.Ufl.Edu, 2021, 
http://users.stat.ufl.edu/~winner/datasets.html. Accessed 20 Feb 2021.

T. Covassin, C.B. Swanik, M.L. Sachs (2003). "Sex Differences and the Incidence of Concussions Among Collegiate Athletes", Journal
of Athletic Training, Vol. (38)3, pp238-244